% !TeX root = ../main.tex
% !TeX spelling = EN_gb


\chapter{Introduction}

This thesis describes the exploration of a method to measure the size and concentration of atmospheric liquid water, aiming to find a cost efficient technique for the detection of the conditions for icing on structures. The chosen measurement method is based on digital image processing and a shadowgraph imaging system using a \gls{led} as background illumination. A prototype instrument was manufactured; components were selected to faciliate low-cost volume production. The applications of a commercial instrument based on this technique are e.g. real-time in-situ icing condition measurements and assimilation and verification of data in numerical weather models. 

Paper I describes a shadowgraph system that uses edge detection to define a measurement range depending on the size of a particle and the image \gls{snr}. Paper II describes the size measurement method, an evaluation of the instrument's  physical design with weather protection and a measurement of LWC and MVD in a purpose-built fog chamber. Paper III describes a verification of the size measurement using polymer microspheres in calibrated distributions traceable from the \gls{nist} and a field study of \gls{lwc} and \gls{mvd} close to the ground using the \gls{dii} and a comparative study using the \gls{cdp}.

\section{Atmospheric Water and Icing}

Measuring or controlling the properties of a fog of water droplets has been of interest and the focus of many studies for at least half a century. Applications can be found in a variety of fields, such as atmospheric studies, aircraft and road traffic safety, medicin, infrastructure, and military. When a mass of air is saturated with water vapour the abundant water will be in either liquid or solid form. In order for water to freeze, or change from liquid to solid state, it needs to be below zero degrees Celsius at the standard atmospheric pressure (273.15 K at 101.325 kPa). For an ice crystal to form in the atmosphere, unless the temperature is below -40°C, the presence of an ice nucleus is also required. If no ice nucleus is present, the water droplet will remain liquid but supercooled. In this state, the water freezes very quickly when it comes in contact with a cold surface. The icing is called in-cloud icing, freezing rain or wet snow icing, depending on the size of the droplets. Combinations of these weather conditions are common.

Icing caused by freezing atmospheric water can be a critical problem in cold climates, affecting infrastructure such as wind turbines, power lines, road and air traffic. With the increasing importance of electric power generated by wind, there is a demand for predictions of icing on wind turbines. Icing on the blades of a turbine lowers the efficiency, increases noise and may force the turbine to a complete stop \cite{dalili2009,cost727,homo2012,jasin1998}. Aircraft, power lines, as well as any other weather exposed structure, share this problem. Efforts have been made to create models for how the ice is formed \cite{makk2000,makk2001,shin1992} and how it can be included in weather prediction models \cite{thomp2009,kring2011}. The severity of the icing depends on many factors, e.g. the duration, the shape and surface of the structure, the wind speed, the atmospheric concentration of liquid water, the \gls{dsd} and the mix of ice and snow \cite{kring2011,makk2000,makk2001,homo2010,han2012}. Of particular interest for the prediction of effect loss on a wind turbine is the phase of ice accretion \cite{davis2014}.

The Liquid Water Content (\gls{lwc}) in atmospheric studies is usually given in either $\mathrm{g\cdot m^{-3}}$ \cite{sein1998} or as the mass quote of water and air $\mathrm{g\cdot kg^{-1}}$. The \gls{dsd} when considering the collision efficiency is most effectively estimated by the Median Volume Diameter (\gls{mvd}) \cite{fins1988}. The \gls{mvd} is the point in the \gls{dsd} where half of the total amount of water in the \gls{dsd} is above the diameter, while the other half is below. Weather models today include the \gls{lwc} and the \gls{mvd}, making it possible to estimate the risk of icing based on general weather data \cite{thomp2009}. The \gls{lwc} and the \gls{mvd} at ground level greatly depends on the local geographical topology, and measurements using in situ instruments are quite rare. There have been attempts to verify \gls{nwp} models using in-situ data \cite{berg2013}. The \gls{lwc} and the \gls{mvd} can be estimated by analyzing satellite or radar images, but a precise estimation of the \gls{dsd} based on radar reflectivity is difficult. The difficutly is partly explained by \gls{dsd} modelling errors, but also by errors originating from the in-situ measurement probes currently used for verification of the models \cite{miles2000}. 

In-situ measurements are rarely simple or straightforward, especially considering the occurance of the mixed conditions mentioned. Despite the development of various measurement techniques and instruments, in-situ measurements are still quite rare due to the cost and most instruments to some extent requiring installation expertize, maintenance and periodic calibration.

\section{Justification and Narrative}

Regions where icing events or periods with temperatures below the standard operational limits occur are of great interest for the installation of wind power. About one third of the global installed wind power capacity is located in what is considered as cold climates, where icing of rotor blades is one of the major challenges \cite{iea2017}.

The work leading to this thesis started with an open mindset and a goal to find a method to detect icing on wind turbines by measuring the optical properties of liquid water in clouds. The reflectance and the absorption of light change depending on the wavelength. The absorption of light is comparatively high for some wavelengths in near and far infrared, but low in the visible blue and green. Clouds consist of water droplets, but the absorption is a function of the travelled distance, which makes it very small in small droplets. Most of the light will be scattered, which is why clouds appear gray at a distance. Light with strong coherence, like that from lasers, will be affected by interference. Coherent and incoherent light sources in wavelengths from visible (450 nm) to near infrared (850 nm) were tested. Illumination angles were tested from 90 (sideways) to 180 (backlit) degrees. After evaluating the different techniques, 180 degrees backlit illumination using blue \gls{led} was selected.

Optical measurement of water droplets has been researched and resulted in numerous publications in the last decades. Shadowgraphy is also used in particle velocimetry, to analyze sprays in various applications. While much has been published on these subjects, there is no instrument readily available that is affordable, reliable and possible to operate near the highest point where icing usually occurs, e.g. one hundred meters up on a wind turbine, or a mast. An instrument for measuring icing parameters for wind turbines should both be able to detect supercooled cloud droplets from five to a few hundred micrometers in diameter and be able to determine the concentration to get an accurate measure of the \gls{lwc}.

The Droplet Imaging Instrument (\gls{dii}) was designed to find a simple, cost effective and robust technique to measure \gls{lwc} and \gls{mvd} in order to predict icing on structures. An automatic sensor based on this technique could be used to trigger ice protection systems used for wind turbines in cold climates \cite{lamra2013}. It was calibrated using a micrometer dot scale with dots of verified sizes printed on a transparent glass. The sizing is verified using four samples of polymer microspheres, calibrated in turn by the National Institute of Standards and Technology (\gls{nist}). The functional simplicity and robustness of the \gls{dii} makes it possible to mass produce and distribute Internet connected instruments based on this technique on a larger geographical scale.

During the winter of 2016-2017, the prototype instrument was placed on the Klövjö mountain, Sweden, at one of the \gls{smhi}'s measuring stations, position 62°29'41''N, 14°9'27''E, 802 meters above sea level. Measurements are available from November 2016 to March 2017. Results from this measurement together with a parallel measurement of \gls{lwc} and \gls{mvd} using a Cloud Droplet Probe \gls{cdp}-2 (\gls{cdp}) from \gls{dmt} are presented in Paper III as well as in this thesis.

\section{Related Work of Measurement}
\label{sec:relwork}
In 1970, Knollenberg \cite{knoll1970} described an electro-optical technique to measure cloud and precipitation particles using a laser illuminated linear array of photo detectors. The photo detectors are used to make a two-dimensional image of the particles’ shadows as they pass the light beam. Systems based on this technique are called \gls{oap}s or two-dimensional imaging probes. Development of this technique include using image sensors to save gray scale images of the detected particles \cite{kulk2011,wend2013}. The \gls{dii} developed and described in this thesis is based on this technique.

Light scattered from a focused laser \cite{baum1983,dye1984} is another technique that can be used to measure single particles, where a laser beam illuminates passing particles. When a particle is detected, its size is determined by comparing the variations in light with a pattern derived from the Mie scattering solutions \cite{mie1908}. The \gls{cdp} used as a reference instrument, is based on this technique.

The \gls{oap}, imaging and the light scattering spectrometers each have advantages over the other technique depending on the nature of the aerosol. E.g. an instrument that can measure micrometer-sized droplets may not be useful for finding large drops or snowflakes. For accurate airborne measurements of \gls{lwc}, \gls{mvd}, and ice content, several instruments and techniques are often combined in a single probe \cite{baum2001, baum2011}.

An optical technique that is very similar to shadowgraphic imaging is based on in-line holography \cite{laws1995}. In principle this is a shadowgraph imaging system that uses laser background illumination to create two-dimensional images of the diffraction patterns created by the passing particles. These patterns are measured to reconstruct images of the particles. This is a fairly calculation intensive process, which may be one of the reasons why instruments based on this technique are quite rare as of yet \cite{henn2013}. An advantage of the holographic technique is the increased measurement range, i.e. the useable depth in each image \cite{kaikk2014}.

Sizing of the droplets using Mie spectrometry is a complex operation even for coherent light \cite{bohr2008}, and although it is possible to study Mie scattering from white light \cite{ward2008}, the complexity, small droplet size range and sample volume makes it less attractive for this application, as the optical resolution is usually too low. This also makes it difficult to determine the exact particle size and the usable depth of field for incoherent shadowgraph systems. The shadow from a particle can e.g. appear smaller or larger when out of focus.

Shadowgraph imaging of particles using incoherent illumination instead of laser has been tried e.g. in particle shadow velocimetry (PSV) \cite{este2005}, or spray characterization \cite{will2010}. There are quantitative and comprehensive studies of other droplet measurement techniques \cite{dye1984,henn2013,conno2007}.

Kuhn et. al. \cite{kuhn2012} have described a method to characterize ice particles using Fourier shape descriptors \cite{gran1972,walla1980}. This system uses a microscope-like technique to achieve a high resolution level, in the order of one micrometer. Athough not specifically designed to measure water droplets, the principal design is similar to the \gls{dii}. 



