% !TeX root = ../main.tex
% !TeX spellcheck = en_Gb

\chapter{Acknowledgements}

I would like to express the greatest gratitude to my supervisor, Benny Thörnberg, for his trust and encouragement especially when things did not turn out the way they were expected.
I would also like to thank Mattias O'Nils and Claes Mattsson at the Department of Electronics Design for making the project possible and giving me the possibility to finish the thesis. 

I owe a big thanks to the Swedish Energy Agency for funding most of the work; Patrik Jonsson, Björn Ollars and Olof Carlsson at Combitech for their work with integration of the CDP; and Esbjörn Olsson at SMHI for sharing his knowledge about the weather physics and his work with the NWP model data.

To my wonderful family; the greatest love and gratitute that have sacrificed a lot and supported me in beginning, fulfilling and finishing this work. Without you this would not have been possible.

Special thanks to Lotta Frisk, Fanny Burman, Carolina Blomberg, Christine Grafström and Maria Rumm for all the administrative work, inspiration and positive energy at the department of Electronics Design.

Not forgetting my mentor Magnus Engström, Göran Tungström, Börje Norlin, David Kraphol, Kent Bertilsson, Henrik Andersson, Javier Brugés, Najeem Lawal, Igor Fedorov, Irida Shallari, Anwar Qaiser, Krister Aldén, Muhammad Imran, Hiba Alqaysi, Jan Thim, Enkeleda Balliu, Muhammad Abu Bakar, Amir Yousuf, Johan Sidén and everyone else at the Mid Sweden University that I forgot to mention. Finally big thanks to Lisa Velander for doing the language review.